Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Distribution and Limits

### 2016-03-10 ms.tex
last of casey's initial comments.

\begin{abstract}
\noindent
The study of clusters of galaxies has been argued to be a very effective way to measure cosmological parameters, including measuring dark energy and testing models of gravity. The Hobby Eberly Telescope Dark Energy Experiment (HETDEX) will observe many hundreds of square degrees, covering a large sample of galaxy clusters out to $z = 0.5$ based on their optical spectra ($3500-5500\AAA$). The spectra will provide important measures of the clusters dynamics and may enable constraints on cosmological parameters, but only if the measurements provide accurate estimates of the total cluster masses. We have carried out a study to investigate the ability of HETDEX to recover accurate galaxy cluster masses over a wide range of masses and redshifts. We used a detailed mock galaxy catalog and present mock observations of two different scenarios: (1) We targeted individual galaxy clusters to investigate the recovery of parameters with such observations. (2) We created and evaluated a HETDEX-like selection "function'' of galaxies over a similarly sized portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass, and benchmark these against observations with perfect knowledge. Using both observing strategies, we produce cluster mass probability density functions $P(X|M,z)$, which can be used to determine the probability that a galaxy cluster of given mass (M), located at redshift ($z$) determined using observable parameter (X). \editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations.}
\end{abstract}

@@

As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters. The goal is to constrain, as best possible, $P(M|x)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$). Generally, cluster mass calibrations fall into two distinct camps, simulation based and direct or statistical calibration.

@@

The second broad camp is the direct calibration of cluster masses. This recipe has two distinct but not always independent tracks. The ``direct'' method uses the direct observations of a small set of clusters and then uses known mass estimators, X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, cosmic microwave background (CMB) observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL) \citeeg{Rozo2010} as examples, which provide a ``true'' mass. This directly calibrates the observable--mass relation which is then applied to a much larger sample. The complications lie in that the ``true'' masses are in fact estimations, and the methods used to recover these masses are subject to their own limitations. X-ray hydrostatic estimations assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses. The Sunyaev--Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up--scattering of CMB photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}. WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters, and potentially suffer from line-of-sight effects as the effect is sensitive to all mass along the line of sight. Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffers from systematics due to cluster formation physics which disrupts the velocity field.

@@

Massive surveys, both on going and planned, are revolutionizing cluster cosmology using a large range of wavelengths. The South Pole Telescope (SPT; \citealt{Carlstrom2011}) and the Atacama Cosmology Telescope (ACT; \citealt{Swetz2011}) are discovering many clusters through the SZE. Optically, the on going The Dark Energy Survey (DES; \citealt{DES2005}) and planned Large Synoptic Survey Telescope (LSST; \citealt{LSST2012}) will identify many thousands of clusters to much lower masses than is possible with SZE measurements. However, regardless of the discovery method used, spectroscopic followup is needed to further constrain $P(X|M,z)$. But as the cluster dataset grows to many tens of thousands of clusters individual followup becomes increasingly impractical. Therefore, large spectroscopic surveys are needed to more fully constrain the observable--mass relation of clusters.

The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) is a trailblazing effort to observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs. Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ from two fields (300 \degsq, Spring field and 120 \degsq, Fall field). Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{ii}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.

While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized ($M_{dyn}\sim 10^{15}$ \msol) clusters at $z<0.5$ (\editorial{talk to casey about how I calculated this number}). The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive. In addition to the recovery of accurate dynamical masses, detailed investigations of the of dynamical state of the clusters is possible.

Connecting the dynamical properties derived from spectroscopy to the properties inferred from other studies insures the greatest impact on future work. HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, the Dark Energy Survey (DES; \citealt{DES2005}), and the upcoming DECam/IRAC Galaxy Environment Survey (DIRGES; PI: Papovich, C. Papovich \etal\ in preparation), the The \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; Papovich \etal\ 2016, ApJS, submitted), and The \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted). While the potential dataset is very rich, two large issues remain.

@@

The ``Buzzard'' mock galaxy catalogs (R. Wechsler et al., private communication) cover 375.68 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses and other various parameters.

Galaxy $M_r$ luminosities are added to the velocity peaks using ShAM \citep{Reddick2013}, and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) assign luminosities in the other bands. A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned. The result is a 398.49 sq. degree mock catalog occupying a $4^h \leq RA \leq 6^h$ and $-61\degree < DEC < -41\degree$ portion of the sky. It contains 238 million galaxies with \sdssr\ mag $< 29$ and $z \leq 8.7$.

@@

We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}. We calculate the HMF is calculated at central redshifts of 0.1, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compared to galaxies in a redshift window of $\Delta z\pm0.01$. We find a very good agreement between the predicted HMF and the observed distribution of clusters. \editorial{Could show a figure comparing the Buzzard catalog to a plot of the HMF for a couple of redshifts. Might be helpful, might not matter.}

@@

To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities. Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted. For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively. For the galaxies in the Buzzard catalog, 1.3\% of the galaxies brighter than $\sdssg = 22$ mag (HETDEX's detection limit) have exactly zero [\ion{O}{ii}] luminosity. Of the 1.3\%, only 3.3\% (0.05\% of all galaxies) have $g-r < 1.5$ suggesting the galaxies which are assigned zero [\ion{O}{ii}] luminosity are not significantly biasing our simulations.

The right panel of Figure~\ref{fig: oii sdss} shows the CMD of all SDSS galaxies. Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by the two colored boxes. The histograms show in the Figure's right panel show the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin around the individual catalog galaxies. We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux. \editorial{We could add a plot like the corner plot to show the multi-dimensionality of this process.}

@@

Tentatively slated to start in the spring of 2016, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator. The 300 \degsq, spring field and 120 \degsq, fall field will have no preselected targets. Using VIRUS on the 10-m Hobby-Eberly Telescope (HET; \citealt{Ramsey1998}) the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.

@@

The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing. This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}. Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next. To cover the 375.67 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU. The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65 slight decreased from the expected filling factor of 1/4.5.

@@

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$. In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known. The 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic. In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements.

\subsection{Dynamical Mass}\label{sec: mass}
The relationship between the LOSVD and dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
\begin{equation}\label{eq:power law}
	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{A_{1D}} \bigg{)}^{1/\alpha} \Msol
\end{equation}
with $A_{1D} = 1177 \pm 4.2$ \kms\ (\citealt{Munari2013}; referred to as $\sigma_{15}$ in \citealt{Evrard2008} and other works), $\alpha = 1/3$, $h(z) = H(z)/100$, and $\sigma_{1D}$ is the LOSVD of the velocity tracers (dark matter particles, subhalos or galaxies).

@@

\subsection{Dynamical Mass Corrections}
In this section we use two methods to predict the mass of a cluster based on other observables. Often the cluster mass is estimated based on a single observable, X-ray temperature, velocity dispersion, richness and others. Here we combine many observables to attempt to correct the mass inferred solely from the velocity dispersion. The first method is traditional probability based where we marginalize over a series of observables to find the most probable mass. The second is based on a machine learning (ML) algorithm which attempts to ``learn'' the relationship between the observables and the desired output, the mass. Both of these methods are examples of supervised learning algorithms where the relationship between the observable (known) parameters and the target parameter (the mass) are both known.

@@

\subsubsection{Probability Based}\label{sec:probability method}
We begin with the training sample. After selecting the desired features $\vec{x} = \{\sigma, z, ...\}$ we make the joint probability between the true cluster mass (M) and $\vec{x}$. Because $\vec{x}$ can be multidimensional, we rely on the ``corner plot'' as an aid to visualize the relationship between all of the training features. Figure~\ref{fig: probability corner} shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.

@@

For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known. To determine the mass probability distribution of a test cluster, $P(M)$ we combine the conditional probability distribution, $P(M|\vec{x})$, created previously with the probability distribution of $\sigma$ through Equation~\ref{eq: Pm}.
\begin{equation}\label{eq: Pm}
	P(M) = \int P(M|\vec{x}) P(\sigma) d\sigma
\end{equation}
The expected mass is determined by integrating the mass probability, $P(M)$ over all mass. This becomes our ``predicted'' mass, $\langle M\rangle$.
\begin{equation}\label{eq: expected mass}
	\langle M\rangle = \int M^\prime P(M^\prime)dM^\prime
\end{equation}
The confidence interval associated with this prediction can be estimated two ways. First, by calculating the variance about the expected mass through
\begin{equation}\label{eq: variance}
	\mathrm{Var} = \int (M^\prime - \langle M\rangle)^2 P(M^\prime)dM^\prime
\end{equation}
or by drawing many samples from $P(M)$ and calculating the values at the 16th and 84th percentile. In practice we find that both methods produce similar results for a large number of trials. Therefore, we quote predicted masses as the most probable mass given by Equation~\ref{eq: expected mass} and associated 68\% error estimated through Equation~\ref{eq: variance}.

@@

Any uncertainties quoted by this method are prediction intervals not confidence intervals. A prediction interval is an estimate of the interval encompassing future observations, with a certain probability. And, unlike confidence intervals, which describe certainties on the different moments of a population, a prediction interval is unique to each prediction. In many regresson analyses, such as linear fitting, the prediction intervals are based on underlying assumptions of normally distributed residuals. However, RF estimators do not have any such assumptions and require special treatment.

@@

Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass. It is important to note that if fewer than five member galaxies are observed $N_{obs} <5$ the cluster is not considered detected, and is excluded from this figure. As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the survey observing strategy across all redshifts and cluster masses.

For the clusters recovered as a function of redshift, there are two effects at work. The decrease in recovery fraction with increasing redshift is a magnitude effect. We check this by limiting the cluster galaxy detection by absolute magnitude which increases the recovery fraction $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold. The second key feature is the strong decline in clusters recovered from survey observations. This is due to gaps in the VIRUS IFU. The median recovery fraction in survey observations is almost exactly 4.5 times less than the targeted median recovery fraction. As the total filling factor of the survey increases the two lines will converge.

The recovery rate as a function of cluster mass, right panel of Figure \ref{fig: recovery}, shows that of the the low mass clusters we detect ($N_{obs} >5$), we observe the majority of the galaxies. This also shows a rapid decrease in the detection fraction, which can again be explained by considering absolute magnitudes instead of apparent magnitudes, as above. Also, high mass clusters are rare, so inorder to detect them we must probe a large volume of space. The higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass. If we were to limit the survey to $z<0.2$ we find the recovery fraction of clusters, at all masses, increases substantially, and we find a much more consistent detection fraction across masses.

@@

For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.37}$ dex and $\mu_{bias} =0.11\pm{0.36}$ dex, respectively. So while, both realistic observations have similar levels of bias, the amount of scatter significantly decreases as more cluster member galaxies are detected, better sampling the LOSVD PDF.

@@

We quantify the bias and scatter for all of the different cluster mass recovery strategies and observing methods in Table \ref{tbl:mass bias}. It should serve as a type of look up table for future cluster observations with HETDEX. The columns represent bins of predicted galaxy cluster mass and the individual values show the bias and scatter of the true cluster mass. The three horizontal sections represent represent perfect, targeted and survey observations respectively. So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M $=13-13.5$ \Msol, it is biased upward by $0.03\pm0.25$ dex.

>>>>

\begin{abstract}
\noindent
The study of clusters of galaxies has been argued to be a very effective way to measure cosmological parameters, including measuring dark energy and testing models of gravity. The Hobby Eberly Telescope Dark Energy Experiment (HETDEX) will observe many hundreds of square degrees, covering a large sample of galaxy clusters to $z < 0.5$ based on their optical spectra ($3500-5500\AAA$). The spectra will provide important measures of the clusters dynamics and may enable constraints on cosmological parameters, but only if the measurements provide accurate estimates of the total cluster masses. We carry out a study to investigate the ability of HETDEX to recover accurate galaxy cluster masses over a wide range of masses and redshifts. We use a detailed mock galaxy catalog and present mock observations of two different scenarios: (1) We targeted individual galaxy clusters to investigate the recovery of parameters with such observations. (2) We created and evaluated a HETDEX-like selection ``function'' of galaxies over a similarly sized portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass, and benchmark these against observations with perfect knowledge. Using both observing strategies, we produce cluster mass probability density functions $P(M|z, X)$, which can be used to determine the probability that a galaxy cluster of given mass (M), located at redshift ($z$) determined using observable parameter (X). \editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations.}
\end{abstract}

@@

As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters. The goal is to constrain, as best possible, $P(M|z, X)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$). Generally, cluster mass calibrations fall into two distinct camps, simulation based and direct or statistical calibration.

@@

The second broad camp is the direct calibration of cluster masses. This recipe has two distinct but not always independent tracks. The ``direct'' method uses direct observations of a small set of clusters and then uses known mass estimators, X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, cosmic microwave background (CMB) observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass. This directly calibrates the observable--mass relation which is then applied to a much larger sample. The complications lie in that the ``true'' masses are in fact estimations, and the methods used to recover these masses are subject to their own limitations. X-ray hydrostatic estimations assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses. The Sunyaev--Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up--scattering of CMB photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}. WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters, and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight. Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffers from systematics due to cluster formation physics which disrupts the velocity field.

@@

Massive surveys, both on going and planned, are revolutionizing cluster cosmology using a large range of wavelengths. The South Pole Telescope (SPT; \citealt{Carlstrom2011}) and the Atacama Cosmology Telescope (ACT; \citealt{Swetz2011}) are discovering many clusters through the SZE. Optically, the on going Dark Energy Survey (DES; \citealt{DES2005}) and planned Large Synoptic Survey Telescope (LSST; \citealt{LSST2012}) will identify many thousands of clusters to much lower masses than is possible with SZE measurements. However, regardless of the discovery method used, spectroscopic followup is needed to further constrain $P(M|z,X)$. But as the cluster dataset grows to many tens of thousands of clusters individual followup becomes increasingly impractical. Therefore, large spectroscopic surveys are needed to more fully constrain the observable--mass relation of clusters.

The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) is a trailblazing effort to observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs. Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field). Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{ii}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.

While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized ($M_{dyn}>10^{15}$ \msol) clusters at $z<0.5$ (\editorial{talk to casey about how I calculated this number}). The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive. In addition to the recovery of accurate dynamical masses, detailed investigations of the of dynamical state of the clusters is possible.

Connecting the dynamical properties derived from spectroscopy to the properties inferred from other studies insures the greatest impact on future work. HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, DES, and the upcoming DECam/IRAC Galaxy Environment Survey (DIRGES; PI: Papovich, C. Papovich \etal\ in preparation), the \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; Papovich \etal\ 2016, ApJS, submitted), and the \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted). While the potential dataset is very rich, two large issues remain.

@@

The ``Buzzard'' mock galaxy catalogs (R. Wechsler et al., private communication) cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses and other various parameters.

Galaxy $M_r$ luminosities are added to the velocity peaks using ShAM \citep{Reddick2013}, and ADDSEDs assign luminosities in the other bands. A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned. The result is a 398.49 \degsq\ mock catalog containing 238 million galaxies with $\sdssr < 29$ mag and $z \leq 8.7$.

@@

We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}. We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compared to galaxies in a redshift window of $\Delta z\pm0.01$. We find a very good agreement between the predicted HMF and the observed distribution of clusters. \editorial{Could show a figure comparing the Buzzard catalog to a plot of the HMF for a couple of redshifts. Might be helpful, might not matter.}

@@

To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities, the right panel of Figure \ref{fig: oii sdss}. Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted. For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively. For the galaxies in the Buzzard catalog, 1.3\% of the galaxies brighter than $\sdssg = 22$ mag (HETDEX's detection limit) have exactly zero [\ion{O}{ii}] luminosity. Of the 1.3\%, only 3.3\% (0.05\% of all galaxies) have $g-r < 1.5$ suggesting the galaxies which are assigned zero [\ion{O}{ii}] luminosity are not significantly biasing our simulations.

The left panel of Figure~\ref{fig: oii sdss} shows the CMD of all SDSS galaxies. Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by the two colored boxes. The histograms show in the Figure's right panel show the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin around the individual catalog galaxies. We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux. \editorial{We could add a plot like the corner plot to show the multi-dimensionality of this process.}

@@

Tentatively slated to start in the spring of 2016, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator. The 300 \degsq, spring field and 120 \degsq\ fall field will have no preselected targets. Using VIRUS on the 10-m Hobby-Eberly Telescope \citep{Ramsey1998} the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.

@@

The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing. This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}. Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next. To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU. The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65 slightly decreased from the expected filling factor of 1/4.5.

@@

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$. In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known. The 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic. In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in future observations of real clusters.

\subsection{Dynamical Mass from Scaling Relations}\label{sec: mass}
The relationship between the LOSVD and dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
\begin{equation}\label{eq:power law}
	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{A_{1D}} \bigg{)}^{1/\alpha} \Msol
\end{equation}
with $A_{1D} = 1177 \pm 4.2$ \kms\ (\citealt{Munari2013}; referred to as $\sigma_{15}$ in \citealt{Evrard2008} and other works), $\alpha = 1/3$, $h(z) = H(z)/100$, and $\sigma_{1D}$ is the LOSVD of the velocity tracers (dark matter particles, subhalos or galaxies). $H(z) = H_0 E(z)$ and $E(z) = \sqrt{\Omega_m(1+z^3)+\Omega_{\Lambda}}$.

@@

\subsection{Other Estimates of Dynamical Mass}
In this section we use two methods to predict the mass of a cluster based on other observables. Often the cluster mass is estimated based on a single observable, X-ray temperature, velocity dispersion, richness and others. Here we combine many observables to attempt to correct the mass inferred solely from the velocity dispersion. The first method is traditional probability based where we marginalize over a series of observables to find the most probable mass. The second is based on a machine learning (ML) algorithm which attempts to ``learn'' the relationship between the observables and the desired output, the mass. Both of these methods are examples of supervised learning algorithms where the relationship between the observable parameters and the target parameter (the mass) are both known.

@@

\subsubsection{Probability Based}\label{sec:probability method}
We begin with the training sample. After selecting the desired features $\vec{x} = \{\sigma, z, ...\}$ we make the joint probability between the true cluster mass (M) and $\vec{x}$. Because $\vec{x}$ can be multidimensional, we rely on the ``corner plot'' as an aid to visualize the relationship between all of the training features. Figure~\ref{fig: probability corner}, a corner plot, shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.

@@

For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known. To determine the mass probability distribution of a test cluster, $P(M)$, we combine the conditional probability distribution, $P(M|\vec{x})$, created previously with the probability distribution of $\sigma$ through Equation~\ref{eq: Pm}.
\begin{equation}\label{eq: Pm}
	P(M) = \int P(M|\vec{x}) P(\sigma) d\sigma
\end{equation}
The expected mass is determined by integrating the mass probability, $P(M)$ over all mass. This becomes our ``predicted'' mass, $\langle M\rangle$.
\begin{equation}\label{eq: expected mass}
	\langle M\rangle = \int M^\prime P(M^\prime)dM^\prime
\end{equation}
The confidence interval associated with this prediction can be estimated two ways. First, by calculating the variance about the expected mass through
\begin{equation}\label{eq: variance}
	\mathrm{Var} = \int (M^\prime - \langle M\rangle)^2 P(M^\prime)dM^\prime
\end{equation}
or by drawing many samples from $P(M)$ and calculating the values at the 16th and 84th percentile. In practice we find that both methods produce similar results for a large number of trials. Therefore, we quote predicted masses as the most probable mass given by Equation~\ref{eq: expected mass} and associated 68\% error estimated through Equation~\ref{eq: variance}.

@@

Any uncertainties quoted by this method are prediction intervals not confidence intervals. A prediction interval is an estimate of the interval encompassing future observations, with a certain probability. And, unlike confidence intervals, which describe uncertainties on the different moments of a population, a prediction interval is unique to each prediction. In many regresson analyses, such as linear fitting, the prediction intervals are based on underlying assumptions of normally distributed residuals. However, RF estimators do not have any such assumptions and require special treatment.

@@

Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass. It is important to note that if fewer than five member galaxies are observed ($N_{obs} <5$) the cluster is not considered detected, and is excluded from this figure. As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the survey observing strategy across all redshifts and cluster masses.

For the clusters recovered as a function of redshift, there are two effects at work. The decrease in recovery fraction with increasing redshift is a magnitude effect. We check this by limiting the cluster galaxy detection by absolute magnitude which increases the recovery fraction to $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold. The second key feature is the strong decline in clusters recovered from survey observations. This is due to gaps in the VIRUS IFU. The median recovery fraction in survey observations is almost exactly 4.5 times less than the targeted median recovery fraction. As the total filling factor of the survey increases the two lines will converge.

The recovery rate as a function of cluster mass, right panel of Figure \ref{fig: recovery}, shows that of the the low mass clusters we detect ($N_{obs} >5$), we observe the majority of the galaxies. This also shows a rapid decrease in the detection fraction, which can again be explained by considering absolute magnitudes instead of apparent magnitudes, as above. Also, high mass clusters are rare, so in order to detect them we must probe a large volume of space. The higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass. If we were to limit the survey to $z<0.2$ we find the recovery fraction of clusters, at all masses, increases substantially, and we find a much more consistent detection fraction across all masses.

@@

For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.37}$ dex and $\mu_{bias} =0.11\pm{0.36}$ dex, respectively. So for the clusters that we detect with survey observations, we obtain similar levels of accuracy as to the targeted observations, on the average. This does not mean that the survey observations cannot be improved by targeted observations. In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD PDF. The targeted observations performs similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.

@@

We quantify the bias and scatter for all of the different cluster mass recovery strategies and observing methods in Table \ref{tbl:mass bias}. It should serve as a type of look up table for future cluster observations with HETDEX. The columns represent bins of predicted galaxy cluster mass and the individual values show the bias and scatter of the true cluster mass. The three horizontal sections represent perfect, targeted and survey observations respectively. So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M $=13-13.5$ \Msol, it is biased upward by $0.03\pm0.25$ dex.
